`SimSurvey`: an `R` package for comparing the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2019-12-29 analysis/paper/sim_survey_paper.Rmd
Address Greg's comments/edits on the revision

Fish populations often show complex spatial and temporal dynamics, creating challenges in designing and implementing effective surveys. Inappropriate sampling designs can potentially lead to both under-sampling (reducing precision and increasing the risk of bias) and over-sampling (through the extensive and potentially expensive sampling of correlated metrics). For assessments based on fisheries-independent surveys, the ability to estimate population parameters is affected by multiple levels of sampling, such as the number of sampling stations as well as the sub-sampling of fish captured to measure biological characteristics (e.g. lengths or ages). Population estimates are also affected by the pathway taken to analyze such data. Though simulations are a useful tool for exploring the efficacy of specific sampling strategies and statistical methods, there are a limited the number of tools that facilitate the simulation testing of a range of sampling and analytical pathways for fisheries-independent survey data. Here we introduce the `R` package **`SimSurvey`**, which has been designed to simplify the process of simulating surveys of age-structured and spatially-distributed fish populations. The package allows the user to simulate age-structured populations that vary in space and time and explore the efficacy of a range of built-in or user-defined sampling protocols to reproduce the population parameters of the known population. **`SimSurvey`** also includes a function for estimating the stratified mean and variance of the simulated data. **`SimSurvey`** can serve as a convenient, accessible and flexible platform for simulating a wide range of sampling strategies for fish stocks that show complex structuring. Various statistical approaches can then be applied to the results to test the efficacy of different analytical approaches.

@@

In this section, we describe the framework currently implemented in the **`SimSurvey`** package. With this framework, we tried to strike a balance between realism, simplicity, generality and computational feasibility. The framework follows four general steps: 1) simulate a spatially-aggregated age-structured population; 2) distribute the population throughout a spatial grid, imposing correlation across space, time and age; 3) sample the population using random sampling; and, 4) obtain population estimates using a design-based analysis. Though there is a degree of flexibility in each of these steps, keep in mind that users can circumvent specific components by applying user defined equations, inputs and/or analyses. Details on how to use the package and circumvent some aspects of its structure are outlined in the **[Using **`SimSurvey`**]** section.

@@

Though some typical relationships have yet to be implemented (e.g. stock-recruitment), this formulation facilitates the simulation of age-structured populations that are dynamic enough to test an array of survey designs.

@@

Rather than developing a full spatially-explicit model, population and spatial dynamics are modeled as independent processes for simplicity. The complexities of spatial population dynamics - such as larval dispersal, spatial differences in growth and meta-population connectivity - are therefor not accounted for and, as such, the model is a substantial simplification of reality. Despite this limitation, the approach taken facilitates the simulation of spatial, age-structured populations with sufficient complexity for testing the efficacy of various survey designs. The simplicity also limits the number of unknown parameters that need to be specified to simulate a population. Parameter estimates from  spatially-aggregated age-structured models, which are commonly used in stock assessments, can therefore be used to simulate a population using the cohort model and the resultant abundance at age values can be distributed across a spatial grid. Here, a grid of $s$ cells is generated where each cell has an area of $A$ and depth $d$; depth is defined using a sigmoid curve, applied across longitude only, with a depth range of $[d_{\mathrm{min}}, d_{\mathrm{max}}]$, shelf depth of $d_{\mathrm{shelf}}$ and a shelf width of $w_{\mathrm{shelf}}$. The grid can be divided into two hierarchical levels.  For demonstration purposes, we envision these levels as part of a stratified-random survey within international fishery divisions, i.e., $H_{\mathrm{strat}}$ depth-based strata within $H_{\mathrm{div}}$ divisions (e.g. NAFO or ICES divisions). The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space. This noise term is normalized to sum to 1 to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model:

@@

The final step in the simulation is to sample the simulated population over the age-year-space array generated. The sampling is random or stratified random, emulating real-world surveys conducted by many research institutions around the world. The area of each strata $A_{\mathrm{strat}}$ is calculated and this is used to define the number of sampling stations $H_{\mathrm{sets}}$, hereafter referred to as sets, allocated to one or more strata under a particular set density, $D_{\mathrm{sets}}$ (i.e. $H_{\mathrm{sets}} = A_{\mathrm{strat}}~D_{\mathrm{sets}}$). The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

@@

Where $n_{a,y,s}$ is the number of fish of age $a$ in year $y$ sampled by a set at location $s$, $A_{\mathrm{trawl}}$ indicates the area covered by the trawl, $A_{\mathrm{cell}}$ is the area of a grid cell, and $q_a$ is the catchability coefficient of each age (i.e. the ability of the trawling gear to catch specific age groups). Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. In cases where there are multiple sets in one cell, the population in that cell is split across the sets. While this means that numbers caught in an isolated simulation cannot exceed the numbers in the population, keep in mind that the survey, no matter how intense, is assumed to have no impact on the population from one year to the next.

@@

The **`SimSurvey`** package was written in the programming language `R` [@R] and it holds a series of functions for 1) simulating the abundance and distribution of virtual fish populations with correlation across space, time and age (`sim_abundance`, `sim_distribution`), 2) simulating surveys with a range of sampling strategies and intensities (`sim_survey`), and 3) estimating the stratified mean and variance of simulated survey data (`test_surveys`; Table \@ref(tab:fun)). **`SimSurvey`** relies heavily on functions from the **`data.table`** [@dowle2017], **`raster`** [@hijmans2016] and **`plotly`** [@sievert2018] packages for their efficient data processing, geographic and plotting facilities, respectively. Package documentation has been published online using **`pkgdown`** (https://paulregular.github.io/SimSurvey/) and all the source `R` code behind **`SimSurvey`** is available on GitHub (https://github.com/PaulRegular/SimSurvey). **`SimSurvey`** can be installed via GitHub using the **`remotes`** package:

@@

Here, the `R_vec` object holds 100 years of simulated recruitment values and each run of the `R_fun` function will result in different simulated values using the internal formulation and the parameters supplied to `sim_R`. The other closures included in the package operate in a similar way in that parameter inputs are supplied to the closure and the functions returned by the closure requires inputs such as ages and/or years. This was done to avoid the repeated specifications of key arguments, such as ages and years. Moreover, this approach provides an option for advanced R users inspect and modify the closures implemented in the package to supply custom closures with alternate equations. Also note that each of the closures implemented in the package includes a plot argument such that quick visuals can be obtained using a line of code like this: `sim_R(log_mean = log(500), log_sd = 0.5, plot = TRUE)(years = 1:100)`).

@@

| **Function call**                                       | **Description**                                              | **Symbol**                              |
|:------------------------------------------------------- |:------------------------------------------------------------ | :-------------------------------------- |
| `sim_distribution(`                                     | &nbsp;                                                       | &nbsp;                                  |
| `+  sim,`                                               | Simulated population from `sim_abundance`                    | &nbsp;                                  |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                             | &nbsp;                                  |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                             | &nbsp;                                  |
| `+                   res = c(3.5, 3.5),`                | Grid resolution in x and y dimensions (km) - i.e. cell area  | $A_{\mathrm{cell}}$                     |
| `+                   shelf_depth = 200,`                | Shelf depth (m)                                              | $d_{\mathrm{shelf}}$                    |
| `+                   shelf_width = 100,`                | Shelf width (km)                                             | $w_{\mathrm{shelf}}$                    |
| `+                   depth_range = c(0, 1000),`         | Depth range from coast to slope (m)                          | $[d_{\mathrm{min}}, d_{\mathrm{max}}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                          | $H_{\mathrm{div}}$                      |
| `+                   strat_splits = 2,`                 | Number of times to horizontally split strat                  | &nbsp;                                  |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata                   | &nbsp;                                  |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution            | $\sigma_{\xi}$                          |
| `+                            range = 300,`             | Range of spatial correlation (km)                            | $r$                                     |
| `+                            lambda = 1,`              | Smoothness of spatial correlation                            | $\lambda$                               |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution              | $\varphi_{\xi, \mathrm{age}}$           |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution             | $\varphi_{\xi, \mathrm{year}}$          |
| `+                            group_ages = 5:20,`       | Make space-age-year noise equal across these ages^1^         | &nbsp;                                  |
| `+                            group_years = NULL),`     | Make space-age-year noise equal across these years^1^        | &nbsp;                                  |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)            | $\mu_d$                                 |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)                | $\sigma_d$                              |

@@

The equations outlined in the *[Simulate spatial distribution]* section are used in the `make_grid`, `sim_ays_covar` and `sim_parabola` functions, and these functions are used within `sim_distribution` to distribute a population simulated using `sim_abundance` throughout a grid (Table \@ref(tab:distribution)). The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied as a raster to `sim_distribution` if the same structure structure and correct projection is used. The package includes a manually constructed survey grid of NAFO Subdivision 3Ps off the southern coast of Newfoundland (named `survey_grid`) and the data-raw folder in the GitHub directory includes the data and code used to construct this grid. However, for simplicity, we use `make_grid` to construct a square grid for a default run of `sim_distribution`. Below we generate and plot (Figure \@ref(fig:grid)) a default grid, another grid with the number of strata increased by increasing the number of `strat_splits`, and another with four divisions and a linear depth gradient (the sigmoid curve is forced to be linear when `shelf_width` is set to zero).

@@

```{r grid, out.height = "320px", fig.cap = "Plots produced by `plot_grid` when supplied a raster object produced by `make_grid` a) using default settings, b) settings that increase the number of times depth strata are horizontally split, and c) settings that produce a more linear depth gradient and increase the number of divisions. In these plots, the yellow to purple color gradient represents depth, the thick grey lines delineate divisions and thin white lines delineate strata."}

@@

In addition to supplying objects produced by `sim_abundance` and `make_grid`, the `sim_distribution` function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by tweaking a few parameters in these closures (Figure \@ref(fig:distribution)). Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider `range`) and exhibits stronger correlation across ages than years (i.e. lower `phi_year` and higher `phi_age`). Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years` arguments, respectively, in the `sim_ays_covar` closure. Variance in the size of the clusters can also be modified by changing the `sd` argument in the `sim_ays_covar` function. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe [`%>%`; @bache2014] friendly such that values from one function call are forwarded to the next function (i.e. output from the two calls below are functionally the same though the approach is slightly different).

@@

| **Function call**                   | **Description**                                                         | **Symbol**              |
|:----------------------------------- |:----------------------------------------------------------------------- | :---------------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;                  |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;                  |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;                  |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$                     |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability (age)                        | $x_0$                   |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (length, width; km) - i.e. area covered by a trawl     | $A_{\mathrm{trawl}}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;                  |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{\mathrm{sets}}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{\mathrm{lengths}}$  |
| `+  length_group = 1,`              | Length group bin size for age sampling (cm)                             | $l_{\mathrm{group}}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{\mathrm{ages}}$     |
| `+  age_sampling = "stratified")`   | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;                  |

@@

The function `sim_survey` can be used to simulate data from one survey over a population created using `sim_distribution`. A default function call is described in Table \@ref(tab:survey). The `sim_survey` function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Also note that the `min_sets` argument imposes a minimum of number of sets to conduct per strata, regardless of its allocation given strat area and set density. This argument imposes a useful constraint for generating data to be analyzed using design-based approaches that require more than one value for the calculation of a mean.

@@

The default parameter values used in this package were chosen to emulate  survey data from a specific cod population (see **[S1 Appendix][S1 Appendix: Case study]** for details) and, as such, these values ought to provide a good place to start for another population of cod. In this section we outline a series of recommended steps to take to tailor the default settings to suit another system. Throughout this outline, we also provide some context on how default parameter values were chosen as this information may help guide a users' choices.

>>>>

Fish populations often show complex spatial and temporal dynamics, creating challenges in designing and implementing effective surveys. Inappropriate sampling designs can potentially lead to both under-sampling (reducing precision and increasing the risk of bias) and over-sampling (through the extensive and potentially expensive sampling of correlated metrics). For assessments based on fisheries-independent surveys, the ability to estimate population parameters is affected by multiple levels of sampling, such as the number of sampling stations as well as the sub-sampling of fish captured to measure biological characteristics (e.g. lengths or ages). Population estimates are also affected by the pathway taken to analyze such data. Though simulations are a useful tool for exploring the efficacy of specific sampling strategies and statistical methods, there are a limited the number of tools that facilitate the simulation testing of a range of sampling and analytical pathways for fisheries-independent survey data. Here we introduce the `R` package **`SimSurvey`**, which has been designed to simplify the process of simulating surveys of age-structured and spatially-distributed fish populations. The package allows the user to simulate age-structured populations that vary in space and time and explore the efficacy of a range of built-in or user-defined sampling protocols to reproduce the population parameters of the known population. **`SimSurvey`** also includes a function for estimating the stratified mean and variance of the population from the simulated survey data. **`SimSurvey`** can serve as a convenient, accessible and flexible platform for simulating a wide range of sampling strategies for fish stocks that show complex structuring. Various statistical approaches can then be applied to the results to test the efficacy of different analytical approaches.

@@

In this section, we describe the framework currently implemented in the **`SimSurvey`** package. With this framework, we tried to strike a balance between realism, simplicity, generality and computational feasibility. The framework follows four general steps: 1) simulate a spatially-aggregated age-structured population; 2) distribute the population throughout a spatial grid, imposing correlation across space, time and age; 3) sample the population using random sampling; and, 4) obtain population estimates using a design-based analysis. Though there is a degree of flexibility in each of these steps, users can circumvent specific components by applying user defined equations, inputs and/or analyses. Details on how to use the package and, if desired, circumvent some aspects of its structure are outlined in the **[Using **`SimSurvey`**]** section.

@@

Though some typical relationships have yet to be implemented (e.g. stock-recruitment), this formulation facilitates the simulation of age-structured populations that are dynamic enough to assess survey performance across a range of abundance levels across years and ages.

@@

Rather than developing a full spatially-explicit model, population and spatial dynamics are modeled as independent processes for simplicity. The complexities of spatial population dynamics - such as larval dispersal, spatial differences in growth and population connectivity - are not explicitly accounted for and, as such, the model is a necessary simplification of reality. Despite this limitation, the approach taken facilitates the simulation of spatial, age-structured populations with sufficient complexity for testing the efficacy of various survey designs. The simplicity also limits the number of unknown parameters that need to be specified to simulate a population. Parameter estimates from  spatially-aggregated age-structured models, which are commonly used in stock assessments, can therefore be used to simulate a population using the cohort model and the resultant abundance at age values can be distributed across a spatial grid. Here, a grid of $s$ cells is generated where each cell has an area of $A$ and depth $d$; depth is defined using a sigmoid curve, applied across one spatial axis, with a depth range of $[d_{\mathrm{min}}, d_{\mathrm{max}}]$, shelf depth of $d_{\mathrm{shelf}}$ and a shelf width of $w_{\mathrm{shelf}}$. We use depth as our main stratification variable, but note that any other appropriate stratification variables could be used. The grid can be divided into two hierarchical levels, management divisions and habitat-based survey strata.  For demonstration purposes, we envision these levels as part of a stratified-random survey within international fishery divisions, i.e., $H_{\mathrm{strat}}$ depth-based strata within $H_{\mathrm{div}}$ divisions (e.g. NAFO or ICES divisions, or any other geographically bounded area). The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space. This noise term is scaled to sum to 1 to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model:

@@

The final step in the simulation is to sample the simulated population over the age-year-space array generated. The sampling is random or stratified random, emulating surveys conducted by many research institutions around the world. The area of each strata $A_{\mathrm{strat}}$ is calculated and this is used to define the number of sampling stations $H_{\mathrm{sets}}$, hereafter referred to as sets, allocated to one or more strata under a particular set density, $D_{\mathrm{sets}}$ (i.e. $H_{\mathrm{sets}} = A_{\mathrm{strat}}~D_{\mathrm{sets}}$). The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

@@

Where $n_{a,y,s}$ is the number of fish of age $a$ in year $y$ sampled by a set at location $s$, $A_{\mathrm{trawl}}$ indicates the area covered by the trawl, $A_{\mathrm{cell}}$ is the area of a grid cell, and $q_a$ is the catchability coefficient of each age (i.e. the ability of the trawling gear to catch specific age groups). Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. In cases where there are multiple sets in one cell, the population in that cell is divided across the sets. While this means that numbers caught in an isolated simulation cannot exceed the numbers in the population, keep in mind that the survey, no matter how intense, is assumed to have no impact on the population from one year to the next.

@@

The **`SimSurvey`** package was written in the programming language `R` [@R] and it holds a series of functions for 1) simulating the abundance and distribution of virtual fish populations with correlation across space, time and age (`sim_abundance`, `sim_distribution`), 2) simulating surveys with a range of sampling strategies and intensities (`sim_survey`), and 3) estimating the stratified mean and variance of simulated survey data (`run_strat`; Table \@ref(tab:fun)). **`SimSurvey`** relies heavily on functions from the **`data.table`** [@dowle2017], **`raster`** [@hijmans2016] and **`plotly`** [@sievert2018] packages for their efficient data processing, geographic and plotting facilities, respectively. Package documentation has been published online using **`pkgdown`** (https://paulregular.github.io/SimSurvey/) and all the source `R` code behind **`SimSurvey`** is available on GitHub (https://github.com/PaulRegular/SimSurvey). **`SimSurvey`** can be installed via GitHub using the **`remotes`** package:

@@

Here, the `R_vec` object holds 100 years of simulated recruitment values and each run of the `R_fun` function will result in different simulated values using the internal formulation and the parameters supplied to `sim_R`. The other closures included in the package operate in a similar way in that parameter inputs are supplied to the closure and the functions returned by the closure requires inputs such as ages and/or years. This was done to avoid the repeated specifications of key arguments, such as ages and years. Moreover, this approach provides an option for advanced R users to inspect and modify the closures implemented in the package to supply custom closures with alternate equations. Also note that each of the closures implemented in the package includes a plot argument such that quick visuals can be obtained using a line of code like this: `sim_R(log_mean = log(500), log_sd = 0.5, plot = TRUE)(years = 1:100)`).

@@

| **Function call**                                       | **Description**                                              | **Symbol**                              |
|:------------------------------------------------------- |:------------------------------------------------------------ | :-------------------------------------- |
| `sim_distribution(`                                     | &nbsp;                                                       | &nbsp;                                  |
| `+  sim,`                                               | Simulated population from `sim_abundance`                    | &nbsp;                                  |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                             | &nbsp;                                  |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                             | &nbsp;                                  |
| `+                   res = c(3.5, 3.5),`                | Grid resolution in x and y dimensions (km) - i.e. cell area  | $A_{\mathrm{cell}}$                     |
| `+                   shelf_depth = 200,`                | Shelf depth (m)                                              | $d_{\mathrm{shelf}}$                    |
| `+                   shelf_width = 100,`                | Shelf width (km)                                             | $w_{\mathrm{shelf}}$                    |
| `+                   depth_range = c(0, 1000),`         | Depth range from coast to slope (m)                          | $[d_{\mathrm{min}}, d_{\mathrm{max}}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                          | $H_{\mathrm{div}}$                      |
| `+                   strat_splits = 2,`                 | Number of strata within each depth class                     | &nbsp;                                  |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata                   | &nbsp;                                  |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution            | $\sigma_{\xi}$                          |
| `+                            range = 300,`             | Range of spatial correlation (km)                            | $r$                                     |
| `+                            lambda = 1,`              | Smoothness of spatial correlation                            | $\lambda$                               |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution              | $\varphi_{\xi, \mathrm{age}}$           |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution             | $\varphi_{\xi, \mathrm{year}}$          |
| `+                            group_ages = 5:20,`       | Make space-age-year noise equal across these ages^1^         | &nbsp;                                  |
| `+                            group_years = NULL),`     | Make space-age-year noise equal across these years^1^        | &nbsp;                                  |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)            | $\mu_d$                                 |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)                | $\sigma_d$                              |

@@

The equations outlined in the **[Simulate spatial distribution]** section are used in the `make_grid`, `sim_ays_covar` and `sim_parabola` functions, and these functions are used within `sim_distribution` to distribute a population simulated using `sim_abundance` throughout a grid (Table \@ref(tab:distribution)). The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied as a raster to `sim_distribution` if the same structure structure and correct projection is used. The package includes a manually constructed survey grid of NAFO Subdivision 3Ps off the southern coast of Newfoundland (named `survey_grid`) and the data-raw folder in the GitHub directory includes the data and code used to construct this grid. However, for simplicity, we use `make_grid` to construct a square grid for a default run of `sim_distribution`. Below we generate and plot (Figure \@ref(fig:grid)) a default grid, another grid with the number of strata increased by increasing the number of `strat_splits`, and another with four divisions and a linear depth gradient (the sigmoid curve is forced to be linear when `shelf_width` is set to zero).

@@

```{r grid, out.height = "320px", fig.cap = "Plots produced by `plot_grid` when supplied a raster object produced by `make_grid` a) using default settings, b) settings that increase the number of times depth strata are split, and c) settings that produce a more linear depth gradient and increase the number of divisions. In these plots, the yellow to purple color gradient represents depth, the thick grey lines delineate divisions and thin white lines delineate strata."}

@@

In addition to supplying objects produced by `sim_abundance` and `make_grid`, the `sim_distribution` function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by adjusting a few parameters in these closures (Figure \@ref(fig:distribution)). Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider `range`) and exhibits stronger correlation across ages than years (i.e. lower `phi_year` and higher `phi_age`). Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years` arguments, respectively, in the `sim_ays_covar` closure. Variance in the size of the clusters can also be modified by changing the `sd` argument in the `sim_ays_covar` function. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe [`%>%`; @bache2014] friendly such that values from one function call are forwarded to the next function (i.e. output from the two calls below are functionally the same though the approach is slightly different).

@@

| **Function call**                   | **Description**                                                         | **Symbol**              |
|:----------------------------------- |:----------------------------------------------------------------------- | :---------------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;                  |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;                  |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;                  |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$                     |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability (age)                        | $x_0$                   |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (distance towed, trawl width; km) - i.e. area trawled  | $A_{\mathrm{trawl}}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;                  |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{\mathrm{sets}}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{\mathrm{lengths}}$  |
| `+  length_group = 1,`              | Length group bin size for age sampling (cm)                             | $l_{\mathrm{group}}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{\mathrm{ages}}$     |
| `+  age_sampling = "stratified")`   | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;                  |

@@

The function `sim_survey` can be used to simulate data from one survey over a population created using `sim_distribution`. A default function call is described in Table \@ref(tab:survey). The `sim_survey` function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Also note that the `min_sets` argument imposes a minimum of number of sets to conduct per strata, regardless of its allocation given strata area and set density. This argument imposes a useful constraint for generating data to be analyzed using design-based approaches that require more than one value for the calculation of a mean.

@@

The default parameter values used in this package were chosen to emulate survey data from a specific cod population  (see **[S1 Appendix][S1 Appendix: Case study]** for details) and, as such, these values ought to provide a good place to start for another population of cod or similar groundfish. In this section we outline a series of recommended steps to take in order to tailor the default settings to suit other systems. Throughout this outline, we also provide some context on how default parameter values were chosen as this information may help guide a users’ choices.
